---
title: "Consumer Complaints"
description: |
  This is my analysis of consumer complaints handled by the Consumer Financial Protection Bureau between March and December 2020.
author:
  - name: Lizzie Stricklin
    url: https://example.com/norajones
date: 04-19-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(flexdashboard)
library(tidyverse)
library(plotly)
library(tigris)
library(tmap)
library(tmaptools)
library(leaflet)
library(DT)
complaints <- readRDS("~/github_stricklin/Data-Journalism-Consumer-Complaints/complaints.rds")

states <- tigris::states(cb=T)
complaints3 <- complaints %>%
  count(state)
complaints3_joined <- geo_join(states, complaints3, "STUSPS", "state")

mypalette <- colorNumeric("YlOrRd", domain = complaints3_joined$n)

popup_fcc <- paste0("Consumer Complaints Mar-Dec 2020: ", as.character(complaints3_joined$n))

map <- leaflet(complaints3_joined) %>% 
  addTiles() %>% 
    setView(-98.483330, 38.712046, zoom = 4) %>% 
      addPolygons(data = states, fillColor = ~mypalette(complaints3_joined$n), fillOpacity = 0.9, weight = 0.2, smoothFactor = 0.2, label = popup_fcc) %>% 
        addLegend(pal=mypalette, values=complaints3_joined$n, bins=5, position="bottomright", title="Consumer Complaints Mar-Dec 2020", labFormat=labelFormat(digits=0))
```

The Consumer Financial Protection Bureau has released data from March - December 2020 chronicling "complaints about consumer financial products and services" the bureau has sent to companies for response. According to the CFPB, "Complaints are published after the company responds, confirming a commercial relationship with the consumer, or after 15 days, whichever comes first. Complaints referred to other regulators, such as complaints about depository institutions with less than $10 billion in assets, are not published in the Consumer Complaint Database."

Below is the map detailing the number of complaints sent to companies between March and December 2020. The states with the most consumer complaints were Florida, California, and Texas.

```{r}
map
```

Customer complaints rose over the nine month time span, hitting a peak of 2,182 complaints on December 29.

```{r}
complaints2 <- complaints %>%
  count(date_received)

fig <- plot_ly(complaints2, x = ~date_received, y = ~n, type = 'scatter', mode = 'lines')
fig %>% layout(title = 'Number of Customer Complaints per Day', yaxis=list(title = 'Number of Complaints'), xaxis = list(title='Date Received'))
#fig
```

The majority of complaints were sent to Experian Information Solutions, Inc., Transunion Intermediate Holdings, Inc., and Equifax, Inc. 31% of the complaints were sent to one of 3,040 other companies, each representing less than 1% of the complaint recipients respectively.

```{r}
complaints4 <- complaints %>%
  count(company)

complaints4.0 <- complaints4 %>% filter(n > 4000)
complaints4.1 <- complaints4 %>% filter(n < 4000)
complaints4.2 <- sum(complaints4.1$n)
complaints4.3 <- c("Other",complaints4.2)
complaints5 <- rbind(complaints4.0, complaints4.3)

fig3 <- complaints5 %>% plot_ly(labels = ~company, values = ~n)
fig3 <- fig3 %>% add_pie(hole = 0.6)
fig3 <- fig3 %>% layout(title = "Companies Receiving Complaints in 2020", showlegend = F, xaxis = list(showgrid = FALSE, zerloine = FALSE, showticklabels = FALSE), yaxis = list(showgrid = FALSE, zerloine = FALSE, showticklabels = FALSE))
fig3
```

