---
title: "Flight Analysis"
description: |
  This is my analysis of 2013 data on domestic flights originating in New York.
author:
  - name: Lizzie Stricklin
    url: https://example.com/norajones
date: 04-20-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

#first load the libraries we'll need
library(tidyverse)
library(plotly)
library(nycflights13) # <- make sure to install this package
library(DT)
flights <- nycflights13::flights
```

This bar chart shows the breakdown of flights by airline that originate at JFK airport and are more than 400 minutes in length. Hawaiian Airlines runs the majority of these long flights coming from JFK.

```{r}
#setting up data

flights_by_origin_airtime_agg <- function(x,y)
{
  flights <- flights %>% 
    filter(origin == x) %>% 
      filter(air_time > y) %>% 
        count(carrier)
  return(flights)
}

q7_data <- flights_by_origin_airtime_agg("JFK",400)

#plotting data

fig <- plot_ly(
  data = q7_data,
  x = ~carrier,
  y = ~n,
  type = "bar"
)

fig <- fig %>% 
  layout(title = "Long Flights from JFK")

fig
```

This bar chart shows which destination airports have the most flights with durations of over 400 minutes. Daniel K. Inouye International Airport in Honolulu receives the majority of these long flights.

```{r}
#setting up data

long_flights <- function(y)
{
  flights <- flights %>% 
    filter(air_time > y) %>% 
      count(dest)
  return(flights)
}

q8_data <- long_flights(400)

#plotting data

fig <- plot_ly(
  data = q8_data,
  x = ~dest,
  y = ~n,
  type = "bar"
)

fig <- fig %>% 
  layout(title = "Long Flight Destinations")

fig
```

This donut chart shows the share each airline has of flights with a destination of Daniel K. Inouye International Airport in Honolulu. Flights are nearly evenly shared between Hawaiian Airlines and United Airlines.

```{r}
#setting up data

share_of_flights <- function(x)
{
  flights <- flights %>% 
    filter(dest == x) %>% 
      count(carrier)
  return(flights)
}

q9_data <- share_of_flights("HNL")

#plotting data

fig <- q9_data %>% 
  plot_ly(labels = ~carrier, values = ~n)
fig <- fig %>% add_pie(hole = 0.6)
fig <- fig %>% layout(title = "Flights Heading to Daniel K. Inouye International Airport")

fig
```

This scatterplot shows the relationship between the departure delay and arrival delay of flights heading to Daniel K. Inouye International Airport in Honolulu.

```{r}
#setting up data

HNL_delays <- function(x)
{
  flights <- flights %>% 
    filter(dest == x)
  return(flights)
}

q10_data <- HNL_delays("HNL")

#plotting data

fig <- plot_ly(data = q10_data, x = ~dep_delay, y = ~arr_delay)
fig <- fig %>% layout(title = "Delays in Flights to Daniel K. Inouye International Airport")

fig
```

